Errorless irrationality: removing error-driven components from the inverse base-rate effect paradigm

### 2023-04-17 docs/manuscript.tex
fix links

We have made available the two experiments written in javascript, the analysis code, the raw data, and all other supplementary materials.
Experiment 1 is shared via \href{https://osf.io/auwvt/}{https://osf.io/auwvt/}, and \href{https://github.com/lenarddome/ply216-observational-ibre}{https://github.com/lenarddome/ply216-observational-ibre}.
Experiment 2 is shared via \href{https://osf.io/2tmc4/}{https://osf.io/2tmc4/} and \href{https://github.com/lenarddome/ply222-non-causal-ibreBA}{https://github.com/lenarddome/ply222-non-causal-ibre}.
The main repository that includes this manuscript and links to the materials for the two experiments can be found on \href{https://github.com/lenarddome/pu093-errorless-attentionless-ibre}{https://github.com/lenarddome/pu093-errorless-attentionless-ibre}.

>>>>

We have made available the two experiments written in javascript, the analysis code, the raw data, and all other supplementary materials both on the Open Science Framework and GitHub.
Experiment 1 is shared on \href{https://osf.io/auwvt/}{https://osf.io/auwvt/}, and \href{https://github.com/lenarddome/ply216-observational-ibre}{https://github.com/lenarddome/ply216-observational-ibre}.
Experiment 2 is similarly shared on \href{https://osf.io/2tmc4/}{https://osf.io/2tmc4/} and \href{https://github.com/lenarddome/ply222-non-causal-ibreBA}{https://github.com/lenarddome/ply222-non-causal-ibre}.
The main repository that includes this manuscript and links to the materials for the two experiments can be found on \href{https://github.com/lenarddome/pu093-errorless-attentionless-ibre}{https://github.com/lenarddome/pu093-errorless-attentionless-ibre}.
